The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-02 src/ms.tex
some words about diversity

  Astropy is
  Practical issues: translation of content and documentation, github is not accessible in some countries.
  \item[Long-term / sustained funding for maintaining infrastructure] Software
  and packaging infrastructure includes but not limited to Continuous
  Integration (CI), test plugins, documentation builds, and package delivery.

@@

  operations. This kind of work has low visibility and is not attractive to
  scientists or volunteer contributors; therefore, it is most effective to
  delegate such tasks to paid roles. \astropy secured a three-year grant for
  this but the situation remains uncertain once the grant runs out, as
  infrastructure evolves and requires constant maintenance and upgrades. Some of
  the engineers currently in these roles are also employees of research

>>>>

  The \astropy project aims to be a project that is made up of members at all
  levels (users to contributors to coordinators) with a diverse set of skills,
  backgrounds, and experiences.
  While \astropy is used globally --- TODO figure with analytics --- our user
  community is underrepresented in non-English-speaking or -teaching countries
  and our maintainers and coordinators are fairly narrowly concentrated in the
  United States (US) and Europe.
  The gap in users in many countries is understandable given that much of our
  content and documentation is written in English and therefore only available
  in other languages through imperfect, automated translation services (like
  Google translate).
  The fact that our maintainers and coordinators are generally in the US (even
  then, mostly on the East coast) and Europe is a reflection of where
  institutions have explicitly supported \astropy, and where volunteers have had
  the ability to contribute to the project.
  \item[Long-term and sustained funding for maintaining infrastructure] The
  software and packaging infrastructure within the \astropy Project includes
  (but is not limited to) Continuous Integration (CI), test plugins,
  documentation builds, and package delivery.

@@

  operations.
  This kind of work has low visibility and is not attractive to scientists or
  volunteer contributors; therefore, it is most effective to delegate such tasks
  to paid roles.
  \astropy secured a three-year grant for this but the situation remains
  uncertain once the grant runs out, as infrastructure evolves and requires
  constant maintenance and upgrades.
  Some of the engineers currently in these roles are also employees of research
